Experience Report: Haskell in Computational Biology

### 2012-03-11 mrfy_experience_report.tex
added a bit about runtime performance.

>>>>

On the protein structures for which it was originally designed, SMURF can 
compute the parse of a query sequence to a MRF based on those structures in 
less than 10 seconds on a typical workstation.
However, on somewhat more 
complex protein structures, SMURF may take two to three minutes on the same 
hardware. 
On the most complex protein structures, SMURF exhausts all memory on 
any system we have available, and must be killed. 
In contrast, MRFy's runtime 
for any of these protein structures is typically less than 30 seconds. 
This 
meets the performance goals we had, and means that MRFy is fast enough to scale 
to whole-genome scans.
